\begin{thebibliography}{9999}%\enlargethispage{\baselineskip}
%
\bibitem[1]{1}A.P. Dempster, N.M. Laird, and D.B. Rubin, "Maximum likelihood from incomplete data via the em algorithm", \textsl{Journal of the Royal Statistical Society: Series B}, vol. 39, pp. 1-38, November 1977.
%
\bibitem[2]{2}Y. Weiss, "Bayesian motion estimation and segmentation", \textsl{PhD thesis}, Massachussets Intitute of Technology, May 1998.
%
\bibitem[3]{3}R.C. Hardie, K.J. Barnard, and E.E. Armstrong, "Joint MAP registration and high-resolution image estimation using a sequence undersampled images", \textsl{IEEE Transaction on Image Processing}, vol. 6, pp. 1621-1633, December 1997.
%
\bibitem[4]{4}M. Murgasova, "Tutorial on Expectation-Maximization: Application to Segmentation of Brain MRI", May 2007.
%
\bibitem[5]{5}S. Borman, "The Expectation Maximization Algorithm",January 2009.
%
\bibitem[6]{6}Wikipedia, "Expectation-Maximization algorithm", \url{http://en.wikipedia.org/wiki/Expectation-maximization_algorithm}, June 2009.
%
\bibitem[7]{7}G. McLachlan, and T. Krishnan, "The EM Algorithm and Extensions", \textsl{John Wiley \& Sons}, New York, 1996.
%
\bibitem[8]{8}K. V. Leemput, F. Maes, D. Vandermeulen et al., "Automated model-based tissue classification of MR images of the brain", \textsl{IEEE Transaction on Medical Imaging}, 18(10), pp. 857-908, 1999.
%
\bibitem[9]{9}K. V. Leemput, F. Maes, D. Vandermeulen et al., "Automated model-based bias field correction of MR images of the brain", \textsl{IEEE Transaction on Medical Imaging} 18(10), pp. 885-896, 1999.
%
\bibitem[10]{10}W. M. Wells III, W.E.L. Grimson, R. Kikinis et al., "Adaptative segmentation of MRI data", \textsl{IEEE Transaction on Medical Imaging} 15(4), pp. 429-442, 1996.
%
\bibitem[11]{11}K.M. Pohl et al., "A Hierarchical Algorithm for MR Brain Image Parcellation", \textsl{IEEE Transaction on Medical Imaging} 26(9), pp. 1201-1212, 2007.
%
\bibitem[12]{12}D. Hoa, and A. Micheau, "e-MRI, Magnetic Resonance Imaging physics and technique course on the web", \textsl{http://e-mri.org}, 2007.
%
\bibitem[13]{13}Kitware, "Insight Toolkit", \url{http://www.itk.org/}, 2009.
%
\bibitem[14]{14}N. Tustison, "Nick's N3 ITK Implementation For MRI Bias Field Correction", \url{http://www.insight-journal.org/browse/publication/640}, June 2009.
%
\bibitem[15]{15}Wikipedia, "Multivariate Normal Distribution",\\ \url{http://en.wikipedia.org/wiki/Multivariate_normal_distribution}, June 2009.
%
\bibitem[16]{16}Wikipedia, "Correlation", \url{http://en.wikipedia.org/wiki/Correlation}, June 2009.
%
\bibitem[17]{17}Wikipedia, "Covariance matrix", \url{http://en.wikipedia.org/wiki/Covariance$\_$matrix}, June 2009.
%
\bibitem[18]{18}K.M. Pohl et al., "Automatic Segmentation Using Non-Rigid Registration", \textsl{MICCAI}, 2005.
%
\bibitem[19]{19}J.G. Sled, A.P. Zijdenbos, and A.C. Evans, "A non parametric method for automatic correction of intensity nonuniformity in mri data", \textsl{IEEE Transactions on Medical Imaging} 17(1), pp. 87-97, February 1998.
%
\bibitem[20]{20}Wikipedia, "Full width at half maximum", \url{http://en.wikipedia.org/wiki/Full_width_at_half_maximum}, July 2009.
%
\bibitem[21]{21}B. Zitova, and J. Flusser, "Image registration methods: a survey", \textsl{Image and vision computing} 21, pp. 977-1000, 2003.
%
\bibitem[22]{22}S. Pieper,M. Halle, and R. Kikinis, "3D SLICER", \textsl{Proceedings of the 1st IEEE International Symposium on Biomedical Imaging} 1, pp. 632-635, 2004.
%
\end{thebibliography}
%\vfill
%\begin{flushright}\small Prepared in \LaTeXe\ by RCJ\end{flushright}
