\begin{thebibliography}{9999}%\enlargethispage{\baselineskip}
%
\bibitem[1]{1}A.P. Dempster, N.M. Laird, and D.B. Rubin, "Maximum likelihood from incomplete data via the em algorithm", \textsl{Journal of the Royal Statistical Society: Series B}, vol. 39, pp. 1-38, November 1977.
%
\bibitem[2]{2}Y. Weiss, "Bayesian motion estimation and segmentation", \textsl{PhD thesis}, Massachussets Intitute of Technology, May 1998.
%
\bibitem[3]{3}R.C. Hardie, K.J. Barnard, and E.E. Armstrong, "Joint MAP registration and high-resolution image estimation using a sequence undersampled images", \textsl{IEEE Transaction on Image Processing}, vol. 6, pp. 1621-1633, December 1997.
%
\bibitem[4]{4}M. Murgasova, "Tutorial on Expectation-Maximization: Application to Segmentation of Brain MRI", May 2007.
%
\bibitem[5]{5}S. Borman, "The Expectation Maximization Algorithm",January 2009.
%
\bibitem[6]{6}Wikipedia, "Expectation-Maximization algorithm", \textsl{http://en.wiki.org/wiki/Expectation-maximization$\_$algorithm}, June 2009.
%
\bibitem[7]{7}G. McLachlan, and T. Krishnan, "The EM Algorithm and Extensions", \textsl{John Wiley \& Sons}, New York, 1996.
%
\bibitem[8]{8}K. V. Leemput, F. Maes, D. Vandermeulen et al., "Automated model-based tissue classification of MR images of the brain", \textsl{IEEE Transaction on Medical Imaging}, 18(10), pp. 857-908, 1999.
%
\bibitem[9]{9}K. V. Leemput, F. Maes, D. Vandermeulen et al., "Automated model-based bias field correction of MR images of the brain", \textsl{IEEE Transaction on Medical Imaging} 18(10), pp. 885-896, 1999.
%
\bibitem[10]{10}W. M. Wells III, W.E.L. Grimson, R. Kikinis et al., "Adaptative segmentation of MRI data", \textsl{IEEE Transaction on Medical Imaging} 15(4), pp. 429-442, 1996.

%
\end{thebibliography}
%\vfill
%\begin{flushright}\small Prepared in \LaTeXe\ by RCJ\end{flushright}
